Statically Typed String Sanitation Inside a Python

### 2014-08-20 sanitation-psp14/sanitation-psp14-short.tex
Added contexts.

$\fbox{\inferrule{}{ \trden{e} = \iota}}$
\begin{mathpar}
\inferrule[Tr-Var]
{ }
{ \trden{x} = x}

@@

\begin{thm}[Translation Correctness]\label{thm:trcorrect}
  If $\tctx \vdash e : \stringin{r}$ then there exists an $\iota$ such that $\trden{e} = \iota$, $\iota \sreduces \tstr{s}$,
  and $e \treduces \rstr{s}$.
\end{thm}
\begin{proof}
The proof proceeds by induction on the typing relation for $e$ and an appropriate choich of $\iota$; in each case,
the choice is the syntactic form in $\lambdap$ corresponding to the form under consideration (e.g. choose {\sf replace} when considering {\sf sreplace}).
After the correct choice, the proof proceeds by our type safety theorems and an appeal to the induction hypothesis.
\end{proof}

>>>>

  $\fbox{\inferrule{}{ \trden{e} = \iota \\ \trden{\sigma} = \tau}}$
\begin{mathpar}
\inferrule[Tr-T-String]
{ }
{ \trden{\stringin{r}} = \str }

\inferrule[Tr-T-Arrow]
{ \trden{\sigma_1} = \tau_1 \\ \trden{\sigma_2} = \tau_2 }
{ \trden{\sigma_1 \rightarrow \sigma_2} = \tau_1 \rightarrow \tau_2 }

\inferrule[Tr-T-Set]
{ \trden{\sigma_1} = \tau_1 \\  ... \\ \trden{\sigma_n} = \tau_n}
{ \trden{ \{\sigma_1, \sigma_2 \} } = \{ \tau_1, \tau_2 \} }

\inferrule[Tr-Var]
{ }
{ \trden{x} = x}

@@

\begin{thm}[Translation Correctness]\label{thm:trcorrect}
  If $\tctx \vdash e : \sigma$ then 
  there exists an $\iota$ such that $\trden{e} = \iota$
  and $\trden{\tctx} \vdash \iota : \trden{\sigma}$.
  Furthermore, $e \sreduces v$ and
  $\iota \treduces \dot{v}$ such that
  $\trden{v} = \dot{v}$.
\end{thm}
\begin{proof}
The proof proceeds by induction on the typing relation for $e$ and an appropriate choich of $\iota$; in each case,
the choice is the syntactic form in $\lambdap$ corresponding to the form under consideration (e.g. choose {\sf replace} when considering {\sf sreplace}).
After the correct choice, the proof proceeds by our type safety theorems and an appeal to the induction hypothesis.
\end{proof}
